Implementing DNS in C0

### 2017-11-17 proposal.tex
Goals section finished.

\documentclass{article}
\usepackage[tt=false]{libertine}
\usepackage{mathpartir}
\usepackage{amsthm}
\usepackage[colorlinks=true]{hyperref}
\usepackage{bytefield}
%\usepackage{fullpage}
\usepackage{listings}
\usepackage{microtype}

@@

Who will write this? I can write some, but I don't really know very much. -Jon

@@

\section{Our Project}

@@

Since this project is limited in scope to \Kwd{DNS}, we will not expose the full functionality of the sockets library in our network interface. We will instead focus on the functions that create and work with datagram-based sockets, as all of the network communication needed for \Kwd{DNS} is done via the datagram protocol \Kwd{UDP}. Additionally, to avoid busy-waiting, we will provide a limited interface to the \texttt{poll} function of the \Kwd{C} standard library in much the same way. We believe that this is sufficient to implement our nameserver, but additional library functionality can be added using these methods if necessary.

@@

>>>>

\documentclass{article}
\usepackage[tt=false]{libertine}
\usepackage{mathpartir}
\usepackage{amsthm}
\usepackage[colorlinks=true]{hyperref}
\usepackage{bytefield}
\usepackage{fullpage}
\usepackage{listings}
\usepackage{microtype}

@@

Farzaneh

@@

\section{Our Project}\label{sec:our-project}

@@

Since this project is limited in scope to \Kwd{DNS}, we will not expose the full functionality of the sockets library in our network interface. We will instead focus on the functions that create and work with datagram-based sockets, as most of the network communication needed for \Kwd{DNS} is done via the datagram protocol \Kwd{UDP}. Additionally, to avoid busy-waiting, we will provide a limited interface to the \texttt{poll} function of the \Kwd{C} standard library in much the same way. We believe that this is sufficient to implement our nameserver, but additional library functionality can be added using these methods if necessary.

@@

\subsection{75\%}

Our 75\% goal is to develop a basic \Kwd{DNS} nameserver in \Kwd{C0}. In order to reduce the scope of this project, we restrict the types of resource data (and by extension, the types of queries) that we handle, and we will only provide support for \Kwd{UDP}-based queries. These two restrictions will simplify implementation, but leave enough functionality that we can evaluate our implementation both for correctness and for performance relative to other DNS implementations, as long as we restrict the test queries to those we have implemented.

The bulk of this goal falls into the two components described in \S\ref{sec:our-project}, along with a small ``main'' component that uses these to actually handle queries. Currently, we have unmarshalling functions and about a third of the network library implemented. We expect that the remainder of this goal should go fairly quickly --- marshalling is no harder than unmarshalling, and the network interface is relatively straightforward to implement once we have decided on what functions are necessary and what their arguments should be.

\subsection{100\%}

To extend the above to a 100\% goal, we plan to extend the functionality of our nameserver by adding caching of requests and potentially adding to the types of resource data we support. While a nameserver without caching is not particularly useful, we believe that the portion of code most likely to contain memory errors is in some combination of reading data from the network and parsing that data --- in particular, dealing with message compression. As such, the 75\% goal is a proof of concept that demonstrates that these portions can be implemented safely, while the 100\% goal extends that proof of concept to be more useable (though still more limited than commercially available nameservers). We expect that in going from our 75\% version to the 100\% version, performance (and the scope of allowable queries) will increase and that we will be able to leave our arguments for correctness unchanged.

\subsection{125\%}

We have two potential 125\% goals, depending on the outcome of our 100\% goal. If our nameserver has good performance relative to its competitors, we will work to provide better justification for the correctness of our nameserver, ideally arriving at a proof that statically verifies that all of our memory accesses are safe. In doing this, we will be able to safely turn off bounds checking when running our nameserver, increasing performance through verifying correctness. If instead our performance is very poor (or not helped much by turning off bounds checking), we will work to optimize our nameserver based on the results of performance testing. It is difficult to say what specifically we will do, but we plan to take the general approach of using software like \texttt{perf} to determine what portions of our code are bottlenecks, and trying to make those paths faster.
